%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Abhijith Mundanad Narayanan} \\ \vspace{1pt}
    \small 123-456-7890 $|$ \href{mailto:mailme@abhimundanad.com}{\underline{mailme@abhimundanad.com}} $|$ 
    \href{https://www.linkedin.com/in/abhijith-mundanad-narayanan-phd/}{\underline{linkedin.com/in/jake}} $|$
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {PhD: Electrical Engineering}{KU Leuven, Belgium}
      {ML and AI: regression, feature-based and DNNs in (biomedical) signal processing.}{Dec. 2016 -- Sep. 2021}
    \resumeSubheading
      {Master of Engineering in Signal Processing}{Indian Institute of Science, Bengaluru}
      {Specialization in audio data processing, speech data processing and classification.}{Aug. 2012 -- Jul. 2014}
    \resumeSubheading
      {B.Tech in Electronics and Communication Engineering}{University of Kerala}
      {Specialization in electronics and communication.}{Aug. 2005 -- Jul. 2009}
  \resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Data Scientist}{Feb, 2023 -- Present (2+ years)}
      {\href{https://toqua.ai}{\underline{Toqua}}}{Gent, Belgium}
      \resumeItemListStart
        \resumeItem{Ownership of ship-kernels: from data ingestion, exploration, modeling, validation to deployment of ship performance models.}
        \resumeItem{Data quality monitoring of ship sensor data: Laid the foundations of a data health monitoring framework.}
        \resumeItem{Developing and maintaining data ingestion pipelines from various data collection APIs.}
        \resumeItem{Skills: python, Microsoft Azure, MLOps using mlflow and Azure ML pipelines}
      \resumeItemListEnd

    \resumeSubheading
      {Data Scientist}{Oct. 2021 -- Dec. 2022 (1 year)}
      {\href{https://indigomed.com/}{\underline{Indigo Diabetes}}}{Zwijnaarde, Gent, Belgium}
      \resumeItemListStart
        \resumeItem{Developers of the world’s first implantable Continuous Metabolite Measurement (CMM) sensor.}
        \resumeItem{From sensor data to glucose models: Built end-to-end data pipelines from raw sensor data to glucose prediction models for Indigo’s first CMM sensor. Skills: python, MATLAB}
        \resumeItem{Making sense of sensor data: Used mathematical models and interactive visualizations to investigate and demonstrate fundamental features, patterns, and issues in collected sensor data. Tools: Python, Bokeh, Dash (Plotly), MATLAB.}
      \resumeItemListEnd
      
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
%-------------------------------------------

    \resumeSubheading
      {Information Technology Support Specialist}{Sep. 2018 -- Present}
      {Southwestern University}{Georgetown, TX}
      \resumeItemListStart
        \resumeItem{Communicate with managers to set up campus computers used on campus}
        \resumeItem{Assess and troubleshoot computer problems brought by students, faculty and staff}
        \resumeItem{Maintain upkeep of computers, classroom equipment, and 200 printers across campus}
    \resumeItemListEnd

    \resumeSubheading
      {Artificial Intelligence Research Assistant}{May 2019 -- July 2019}
      {Southwestern University}{Georgetown, TX}
      \resumeItemListStart
        \resumeItem{Explored methods to generate video game dungeons based off of \emph{The Legend of Zelda}}
        \resumeItem{Developed a game in Java to test the generated dungeons}
        \resumeItem{Contributed 50K+ lines of code to an established codebase via Git}
        \resumeItem{Conducted  a human subject study to determine which video game dungeon generation technique is enjoyable}
        \resumeItem{Wrote an 8-page paper and gave multiple presentations on-campus}
        \resumeItem{Presented virtually to the World Conference on Computational Intelligence}
      \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
    \resumeSubHeadingListStart
      \resumeProjectHeading
          {\textbf{Gitlytics} $|$ \emph{Python, Flask, React, PostgreSQL, Docker}}{June 2020 -- Present}
          \resumeItemListStart
            \resumeItem{Developed a full-stack web application using with Flask serving a REST API with React as the frontend}
            \resumeItem{Implemented GitHub OAuth to get data from user’s repositories}
            \resumeItem{Visualized GitHub data to show collaboration}
            \resumeItem{Used Celery and Redis for asynchronous tasks}
          \resumeItemListEnd
      \resumeProjectHeading
          {\textbf{Simple Paintball} $|$ \emph{Spigot API, Java, Maven, TravisCI, Git}}{May 2018 -- May 2020}
          \resumeItemListStart
            \resumeItem{Developed a Minecraft server plugin to entertain kids during free time for a previous job}
            \resumeItem{Published plugin to websites gaining 2K+ downloads and an average 4.5/5-star review}
            \resumeItem{Implemented continuous delivery using TravisCI to build the plugin upon new a release}
            \resumeItem{Collaborated with Minecraft server administrators to suggest features and get feedback about the plugin}
          \resumeItemListEnd
    \resumeSubHeadingListEnd



%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, C/C++, SQL (Postgres), JavaScript, HTML/CSS, R} \\
     \textbf{Frameworks}{: React, Node.js, Flask, JUnit, WordPress, Material-UI, FastAPI} \\
     \textbf{Developer Tools}{: Git, Docker, TravisCI, Google Cloud Platform, VS Code, Visual Studio, PyCharm, IntelliJ, Eclipse} \\
     \textbf{Libraries}{: pandas, NumPy, Matplotlib}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}
